### 2015-01-18 src/related.Rnw
update related

>>>>

Operator and mutant subsumption is another active area of research
for reduction of number of mutants where by operators or mutants
that do not significantly differ from others are eliminated. Kurtz et
al.~\cite{kurtz2014mutant} finds that savings up to 2400\% can be achieved
using subsumption alone, even though the result is based on investigation
of a single program \textit{cal}. Research into subsumption of mutants also
includes Higher Order Mutants, where by multiple mutations are introduced
into the same set of mutants, reducing the total number of individual mutants
by subsuming the component mutants. These have investigated by
Jia et al.~\cite{jia2009higher,jia2008constructing}, and finds that it can
reduce the number of mutants by 50\%.
